### 2023-09-29 thesis/chapters/02-analysis-B-features.tex
Minor changes in template
Refactor MAFAULDA EDA and add experimental sampler for beaglebone

\myequations{DC blocker IIR filter of 1st order}
\begin{equation} \label{equ:iir-dc-blocker}
y_k = (1 - \frac{\omega}{2}) \cdot (x_k  -  x_{k - 1}) + (1 - \omega) \cdot y_{k - 1}; \quad \omega = 2\pi \cdot \frac{f_{3dB}}{f_s}
\end{equation}

@@

If a single principal frequency exists, it can be determined with maximum likelihood estimation. Such frequency would explain the signal spectrum the best~\cite{peeters_large_2004}.  The frequency spectrum is a discrete set of amplitudes where peaks have to be reliably identified to create representative attributes.
The essential peak-finding approaches are based either on magnitude or gradient. All found extrema are commonly filtered with the magnitude of prominences and the widths at half prominence. In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i-1} < x_i > x{i+1}$. The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.

>>>>

\myequations{DC blocker IIR filter of 1st order}
\begin{ceqn}\begin{align} \label{equ:iir-dc-blocker}
y_k = (1 - \frac{\omega}{2}) \cdot (x_k  -  x_{k - 1}) + (1 - \omega) \cdot y_{k - 1}; \quad \omega = 2\pi \cdot \frac{f_{3dB}}{f_s}
\end{align}\end{ceqn}

@@

If a single principal frequency exists, it can be determined with maximum likelihood estimation. Such frequency would explain the signal spectrum the best~\cite{peeters_large_2004}.  The frequency spectrum is a discrete set of amplitudes where peaks have to be reliably identified to create representative attributes.
The essential peak-finding approaches are based either on magnitude or gradient. All found extrema are commonly filtered with the magnitude of prominences and the widths at half prominence. In the magnitude-based method, middle point $x_i$ is compared to neighboring two points and the peak is then: $x_{i-1} < x_i > x_{i+1}$. The gradient-based method evaluates the first derivative at the point which is equal to zero in case the point is a local maximum, local minimum, or inflection point~\cite{adikaram_non-parametric_2016}.
